---
title: "Homework A01: Bayesian Analysis of Dishonesty Detection"
author: "Generated Analysis Report"
date: "`r Sys.Date()`"
format:
  html:
    theme: cosmo
    toc: true
    toc-depth: 2
    number-sections: true
    code-fold: true
---

# Introduction

This document contains the complete analysis for Homework A01: Bayesian Analysis of Dishonesty Detection. The analysis includes combinatorial approaches to understanding possible outcomes under different assumptions about participant honesty, followed by Bayesian inference using observed data.

All code and output are generated directly in this document.

# Environment Setup

```{r setup, message=FALSE, warning=FALSE}
# Set working directory
current_dir <- getwd()
if (!basename(current_dir) == "homework_A01") {
  setwd(file.path(current_dir, "stat_rethinking_2026", "homework", "homework_A01"))
}

# Source setup script
source("scripts/00_setup.R")
```

# Dishonesty Detection Analysis

```{r dishonesty_analysis, message=TRUE, warning=FALSE}
# Run the dishonesty detection analysis
source("scripts/01_dishonesty_detection.R")
```

# Globe Tossing Analysis

```{r globe_tossing, message=TRUE, warning=FALSE}
# Run the comparative globe tossing analysis
source("scripts/02_globe_tossing.R")
```

# Validation Tests

```{r validation, message=TRUE, warning=FALSE}
# Run validation tests if available
if (file.exists("tests/smoke_likelihoods.R")) {
  source("tests/smoke_likelihoods.R")
} else {
  cat("Validation tests not found.\n")
}
```

# Summary

Analysis complete. All output files have been generated in the `output/` directory.

- **Figures**: `output/figures/`
- **Tables**: `output/tables/`
- **Reports**: `output/reports/`
